### 2019-04-24 sections/properties.tex
rename main tex file to main
remove reference to proofs about big step semantics
shorten properties section

In order to validate our semantics, we show that our evaluation, normalisation
and handling semantics is type preserving. We additionally prove a progress
theorem for our small-step handling semantics.

Additionally, we show that the normalisation semantics is a big-step semantics.
%XXX: Alejandro: ?
% Niks meer mee doen, was voor PLDI reviewers duidelijk genoeg. --TS
While at first sight, this might seem obvious, the fact that we are dealing with
state complicates matters.

We show that our failing function $\Failing$ indeed only indicates expressions
that can not be normalised and that allow no further interaction.

Finally, we prove that the function to compute all possible inputs $\Inputs$ is sound and complete.

@@

\Cref{thm:pres-eval} is shown to be correct by induction over $e$. The full
proof can be found in the appendix.

Moving on, we show that normalisation also preserves types, by showing that the following Theorem holds.

@@

Since this semantics makes use of the value function $\Value$ and the striding semantics $\stride$,
we first need to show that preservation also holds for these two semantics.

\begin{lemma}[Task value preserves types]
  % For all well typed expressions $e$ and states $\sigma$,
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers \sigma$,
  if $\Value{(e,\sigma)}=v$,
  then $v:\tau$.
  \label{lem:presvalue}
\end{lemma}

\begin{lemma}[Striding preserves types]
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers \sigma$,
  if $e,\sigma \stride e',\sigma'$,
  then $\Gamma,\Sigma \infers e':\Task\tau$ and $\Sigma \infers \sigma'$.
  \label{thm:pres-stride}
\end{lemma}

\Cref{lem:presvalue} and \cref{thm:pres-stride} are proven in the
appendix by induction over $e$. This subsequently allows us to prove
\Cref{thm:pres-norm}, again by induction over $e$.

This brings us finally to the type preservation property of the handling semantics.

@@

And again, this is proven by induction over $e$.

From \cref{thm:pres-handle} and \cref{thm:pres-norm} we directly
obtain that the driving semantics also preserves types.

@@

If an expression $e$ and state $\sigma$ are well-typed, then after normalisation, the pair $e',\sigma'$
either fails, or there exists some input $i$ that can be handled by it under the handling semantics.
In order to prove this Theorem, we require an additional theorem.

% \paragraph{Failing}

We need to show that the failing function $\Failing$ behaves as desired.

>>>>

In order to validate our semantics, we show that our evaluation, normalisation
and handling semantics is type preserving. We additionally prove a progress
theorem for our small-step handling semantics.
We show that our failing function $\Failing$ indeed only indicates expressions
that can not be normalised and that allow no further interaction.
Finally, we prove that the function to compute all possible inputs $\Inputs$ is sound and complete.

@@

@@

@@

All three Theorems are proven to be correct by induction over $e$.
The full proofs are listed in the appendix.
From \cref{thm:pres-handle} and \cref{thm:pres-norm} we directly
obtain that the driving semantics also preserves types.

@@

If an expression $e$ and state $\sigma$ are well-typed, then after normalisation, the pair $e',\sigma'$
either fails, or there exists some input $i$ that can be handled by it under the handling semantics.
In order to prove this Theorem, we need to show that the failing function $\Failing$ behaves as desired.
